Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/acm/paper.tex
Notes in disc

\numberofauthors{3}

\author{
% 1st. author
\alignauthor
John Burchell\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \affaddr{Gothenburg, Sweden}\\
       \email{john.a.burchell@gmail.com}
% 2nd. author
\alignauthor
William Granli\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \affaddr{Gothenburg, Sweden}\\
       \email{william.granli@gmail.com}
% 3rd. author
\alignauthor Imed Hammouda\titlenote{Co-author}\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \affaddr{Gothenburg, Sweden}\\
       \email{imed.hammouda@gu.se}
}

@@

@@

This leads to the conclusion (!!probably avoid that word in discussion) that the inclusion of new features and the maintainability of an API are two very strong drivers of API evolution.

%%% Notes and thoughts
Consistent with Lehmans Laws - Continuing growth, feedback systems seem to be very important.
Desire from some partners to have more have even more additional features etc
Business rules and motives are not taken into consideration apparently when creating these APIs. They probably should be!

@@

\subsection{RQ2}
The 
The general conclusion: 
5 laws clearly apply
2 laws probably apply (not significant)
1 law clearly doesn't apply

Have a table which relates each theory to each change (after we have re-analysed the one on docs. )

>>>>

\numberofauthors{4}

\author{
% 1st. author
\alignauthor
John Burchell\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \affaddr{Gothenburg, Sweden}\\
       \email{john.a.burchell@gmail.com}
% 2nd. author
\alignauthor
William Granli\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \affaddr{Gothenburg, Sweden}\\
       \email{william.granli@gmail.com}
\and
% 3rd. author
\alignauthor Imed Hammouda\titlenote{Co-author}\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \affaddr{Gothenburg, Sweden}\\
       \email{imed.hammouda@gu.se}
% 4th 
\alignauthor Eric Knauss\titlenote{Co-author}\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \affaddr{Gothenburg, Sweden}\\
       \email{imed.hammouda@gu.se}
}

@@

%Summary of the results (overview)

@@

%The most interesting parts (and reflections + more information about these "trends")
This leads to the conclusion (!!probably avoid that word in discussion) that the inclusion of new features and the maintainability of an API are two very strong drivers of API evolution.

%

%%% Notes and thoughts
%Consistent with Lehmans Laws - Continuing growth, feedback systems seem to be very important.
%Desire from some partners to have more have even more additional features etc
%Business rules and motives are not taken into consideration apparently when creating these APIs. They probably should be!

@@

\subsection{RQ2}
You can't assume
